Gammapy: A Python package for gamma-ray astronomy

### 2023-03-23 src/ms-review.tex

%% Context: development of open software
%% CN: I don't see the parallel between gamma-ray astronomy establishing itself and the success of python
%% maybe this was the introduction of the very first draft?
%% I would just write: "In the past decade, \textit{Python} has become..."
In the past decade, observing the \gammaray sky has transitioned from a niche in the field of
particle physics to an established branch of astronomy, completing the view of the
sky in high energies. At the same time \textit{Python}
has become extremely popular as a scientific programming language,
in particular in the field of data sciences. This success is
mostly attributed to the simple and easy to learn syntax, the ability to act as
a \enquote{glue} language between different programming languages and last but not least
the rich ecosystem of packages and its open and supportive community \citep{Momcheva2015}.

>>>>

%% Context: development of open software
%% CN: I don't see the parallel between gamma-ray astronomy establishing itself and the success of python
%% maybe this was the introduction of the very first draft?
%% I would just write: "In the past decade, \textit{Python} has become..."
In the past decade \textit{Python} has become extremely popular as a scientific programming language,
in particular in the field of data sciences. This success is
mostly attributed to the simple and easy to learn syntax, the ability to act as
a \enquote{glue} language between different programming languages and last but not least
the rich ecosystem of packages and its open and supportive community \citep{Momcheva2015}.
